\texttt{DreamCoder}: Growing libraries of concepts with wake-sleep program induction

### 2018-10-02 pp.tex
progress on presentation

\DeclareMathOperator*{\argmax}{arg\,max}
%Information to be included in the title page:
\title{Growing libraries of concepts with wake-sleep program induction}
\author{Kevin Ellis\\Joint with: Lucas Morales, Mathias Sabl\'e Meyer, Armando Solar-Lezama, Joshua B. Tenenbaum\\Heavy inspiration from: Eyal Dechter}
\institute{MIT} 
\date{October 2018}

@@

\begin{frame}{The Language of Thought}
\begin{tikzpicture}
    \node at (-3,1) {\includegraphics[width = 6cm]{Fodor.jpg}};
  \node at (2,2) {\includegraphics[width = 8cm]{Solomon.png}};
%
    \end{tikzpicture}
\end{frame}

@@

\begin{frame}{Engineering the language of thought}
  \begin{tikzpicture}
    \node at(0,0) {\includegraphics[width = 8cm]{characters.png}};
    \node at(-3,2) {\includegraphics[width = 8cm]{Brendan.jpg}};

@@

\begin{frame}{DreamCoder}
  \begin{itemize}
  \item   \textbf{Wake:} Solve problems by writing programs
  \item \textbf{Sleep:} Improve DSL and neural recognition model:
    \begin{itemize}
    \item \textbf{Sleep-G:} Improve DSL (\textbf{G}enerative model)
      \item \textbf{Sleep-R:} Improve \textbf{R}ecognition model
      \end{itemize}
  \end{itemize}
  Combines ideas from Wake-Sleep \& Exploration-Compression algorithm by Eyal Dechter

@@

\begin{frame}{Symbolic regression from visual input}
\centering\includegraphics[width = 5cm]{symbolicRegression.png}
\end{frame}

>>>>

\DeclareMathOperator*{\argmax}{arg\,max}
%Information to be included in the title page:
\title{\texttt{DreamCoder}: Growing libraries of concepts with wake-sleep program induction}
\author{Kevin Ellis\\Joint with: Lucas Morales, Mathias Sabl\'e Meyer, Armando Solar-Lezama, Joshua B. Tenenbaum\\Heavy inspiration from: Eyal Dechter}
\institute{MIT} 
\date{October 2018}

@@

\begin{frame}{Human program induction everywhere}
\begin{tikzpicture}
  \node(Lisp) at (0,0) {\includegraphics[width = 5cm]{figures/1975.png}};
  \visible<2->{
    \node(colorless) at (6,0) {\includegraphics[width = 5cm]{figures/colorless.png}};
    \node at ([yshift=-2cm]colorless.south) {\includegraphics[width = 4cm]{figures/child.jpg}};
  }
  \visible<3->{
    \node(aqueduct) at ([yshift=-1cm,xshift=0cm]Lisp.south) {\includegraphics[width = 5cm]{figures/aqueduct.jpg}};
    \node(arch) at ([xshift=1cm,yshift=0cm]aqueduct.south) {\includegraphics[width = 1.5cm]{figures/arch.jpg}};
  }
  \visible<4->{
    \node at ([yshift=-1cm,xshift=-2cm]aqueduct.south) {\includegraphics[width = 2cm]{figures/tapestry.jpg}};
    \node(wiringDiagram) at ([yshift=-1cm,xshift=1.6cm]aqueduct.south) {\includegraphics[width = 5cm]{figures/wiringDiagram.jpg}};
  }
  \visible<5->{
    \node at ([xshift=2cm,yshift=1cm]wiringDiagram.east) {\includegraphics[width = 5cm]{tree.jpg}};
    }
  \end{tikzpicture}

@@

\begin{frame}{Human program induction everywhere}
  \begin{tikzpicture}
    \node at(0,0) {\includegraphics[width = 8cm]{characters.png}};
    \node at(-3,2) {\includegraphics[width = 8cm]{Brendan.jpg}};

@@

\begin{frame}{DreamCoder}
  \begin{itemize}
  \item   \textbf{Wake:} Solve problems by writing programs
  \item \textbf{Sleep:} Improve DSL and neural recognition model:
    \begin{itemize}
    \item \textbf{Sleep-G:} Improve DSL (\textbf{G}enerative model)
      \item \textbf{Sleep-R:} Improve \textbf{R}ecognition model
      \end{itemize}
  \end{itemize}
  Combines ideas from Wake-Sleep \& Exploration-Compression algorithm by Eyal Dechter
\Wider[5.4em]{
  \begin{tikzpicture}
    \node at (6,0) {  \includegraphics[width = 4cm]{figures/sleepingChild.jpg}};
    \visible<2->{
      \node(Lisp) at (-3,0) {\includegraphics[width = 3cm]{figures/Lisp.png}};
      \node(tower) at ([xshift=1.5cm]Lisp.east) {\includegraphics[width = 3cm]{figures/pyramid1.png}};
      \node(logo) at ([xshift=1.5cm]tower.east) {\includegraphics[width =3cm]{figures/9logo.png}}; 
    }
    \end{tikzpicture}}

@@

%% \begin{frame}{Symbolic regression from visual input}
%% \centering\includegraphics[width = 5cm]{symbolicRegression.png}
%% \end{frame}
